\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
introduction quelle und 4. quelle

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem in this area is that the situation is getting worse and worse. Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child in the US is about 30 percent - according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. Another recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

@@

\subsection{Open questions}
The game designer and scientist Jane McGonigal, once suffering from depression herself, investigates in several research projects and studies on how gamification can improve people's life and happiness \footnote{\url{http://janemcgonigal.com/learn-me/}}. For this purpose she once created a game SuperBetter to treat herself, leading to the founding of her company SuperBetter Labs. Her experiments show that habits learned during playing a game with real world content can influence people‘s behaviour even after the game already ended. The game \emph{World without Oil} \footnote{\url{http://worldwithoutoil.org/metaabout.htm}} is an alternate reality game to call attention to a possible future oil shortage. People playing this game showed to be more sensitive for sustainable oil usage afterwards. The open question we want to answer is whether gamification can have a similar impact on the long-term attitude of people towards living a healthy life. We want to find out which factors can lead to a success or a failure of this system and how different societies need different motivations factors. \\

>>>>

Recent studies \citep{euobes2003} show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem in this area is that the situation is getting worse and worse. Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child in the US is about 30 percent - according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. Another recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

@@

\subsection{Open questions}
The game designer and scientist Jane McGonigal, once suffering from depression herself, investigates in several research projects and studies on how gamification can improve people's life and happiness \footnote{\url{http://janemcgonigal.com/learn-me/}}. For this purpose she once created a game SuperBetter to treat herself, leading to the founding of her company SuperBetter Labs. Her experiments show that habits learned during playing a game with real world content can influence people‘s behaviour even after the game already ended. The game \emph{World without Oil} \citep{wwoil2007} is an alternate reality game to call attention to a possible future oil shortage. People playing this game showed to be more sensitive for sustainable oil usage afterwards. The open question we want to answer is whether gamification can have a similar impact on the long-term attitude of people towards living a healthy life. We want to find out which factors can lead to a success or a failure of this system and how different societies need different motivations factors. \\
